{\pkg}: A Python Package for Integrating Computational Models Across Languages and Scales

### 2019-01-21 papers/lang2018/ms.tex
Update text with new commands, minor bug fix in server test, todo with links in red

%---------------------------------------------------------------------------------
% CONTROL THINGS
\newcommand{\todo}[1]{{\color{red}{#1}}}
\newcommand{\addref}{{\color{red}(ref. needed)}}
\newcommand{\Msol}{\,M$_{\odot}$}
\newcommand{\TB}{\,Tbytes}
\newcommand{\pkg}{{\tt yggdrasil}{}}
\newcommand{\cis}{{\tt cis\_interface}{}}
\newcommand{\pkglink}{\todo{cis\_interface}}
%\newcommand{\pkg}{{\tt \todo{cis\_interface}}{}}
\newcommand{\pkgrun}{{\tt \todo{cisrun}}}
\newcommand{\A}{Appendix{ }}
\newcommand{\hrefgit}[1]{\href{https://github.com/cropsinsilico/cis_interface}{\todo{#1}}}
\newcommand{\hrefdoc}[1]{\href{https://cropsinsilico.github.io/cis_interface/}{\todo{#1}}}
\newcommand{\hrefhack}[1]{\href{https://cropsinsilico.github.io/cis_interface/hackathon2018/index.html}{\todo{#1}}}

%---------------------------------------------------------------------------------
% SOURCE CODE
\newcommand{\rootsrc}{\lstinputlisting[language=C,label={lst:src:root},caption={root.h: Source code for root model in C.}]{../../cis_interface/examples/root_to_shoot/src/root.h}}
\newcommand{\shootsrc}{\lstinputlisting[language=Python,label={lst:src:shoot},caption={shoot.py: Source code for shoot model in Python.}]{../../cis_interface/examples/root_to_shoot/src/shoot.py}}

%---------------------------------------------------------------------------------
% WRAPPER CODE
\newcommand{\rootwrap}{\lstinputlisting[language=C,label={lst:wrap:root},caption={root\_wrapper.c: Wrapper source code for root model in C.}]{../../cis_interface/examples/root_to_shoot/src/root_wrapper.c}}
\newcommand{\shootwrap}{\lstinputlisting[language=Python,label={lst:wrap:shoot},caption={shoot\_wrapper.py: Wrapper source code for shoot model in Python}]{../../cis_interface/examples/root_to_shoot/src/shoot_wrapper.py}}

%---------------------------------------------------------------------------------
% YAML FILES
\newcommand{\rootyml}{\lstinputlisting[label={lst:yml:root},caption={root.yml: Model YAML specification file for root model.}]{../../cis_interface/examples/root_to_shoot/root.yml}}
\newcommand{\shootyml}{\lstinputlisting[label={lst:yml:shoot},caption={shoot.yml: Model YAML specification file for shoot model.}]{../../cis_interface/examples/root_to_shoot/shoot.yml}}
\newcommand{\rootymlfiles}{\lstinputlisting[label={lst:yml:root_files},caption={root\_files.yml: Connection YAML specification file for running the root model in isolation.}]{../../cis_interface/examples/root_to_shoot/root_files.yml}}
\newcommand{\shootymlfiles}{\lstinputlisting[label={lst:yml:shoot_files},caption={shoot\_files.yml: Model YAML specification file for running the shoot model in isolation.}]{../../cis_interface/examples/root_to_shoot/shoot_files.yml}}
\newcommand{\intyml}{\lstinputlisting[label={lst:yml:int},caption={root\_to\_shoot.yml: Connection YAML specification file for the root/shoot integration.}]{../../cis_interface/examples/root_to_shoot/root_to_shoot.yml}}

@@

We present an Open Source Python package, {\pkg}, for creating and running integration networks by connecting existing computational models written in different programming languages. {\pkg} was developed as part of the Crops \emph{in Silico} \citep{Marshall-Colon2017} initiative to build a complete crop \emph{in silico} from the level of the genes to the level of the field. {\pkg} is available on Github\footnote{{\tt https://github.com/cropsinsilico/\pkglink}} with full documentation\footnote{{\tt https://cropsinsilico.github.io/\pkglink/}} and can be installed from PyPI\footnote{{\tt https://pypi.org/project/\pkglink/}} via {\tt pip install {\pkg}} or conda-forge\footnote{{\tt https://github.com/conda-forge/\pkglink-feedstock}} via {\tt conda -c conda-forge install {\pkg}}. Although developed for the purpose of integrating plant biology models, {\pkg} can be applied to any situation requiring coordination between models in the supported languages. \S\ref{S:background} provides background information on existing efforts for cross-language model integration, \S\ref{S:methods} describes the methods used by the {\pkg} package to integrate models, \S\ref{S:example} provides a worked example of integrating the two model presented above, \S\ref{S:results} presents several tests demonstrating the performance of message passing between integrated models, and \S\ref{S:discuss} describes a few use cases for {\pkg}, 
summarizes the features and limitations of the {\pkg} package, and outlines areas of ongoing and future development.

>>>>

%---------------------------------------------------------------------------------
% CONTROL THINGS
\newcommand{\todo}[1]{{\color{red}{#1}}}
\newcommand{\addref}{{\color{red}(ref. needed)}}
\newcommand{\Msol}{\,M$_{\odot}$}
\newcommand{\TB}{\,Tbytes}
\newcommand{\pkg}{{\tt yggdrasil}{}}
\newcommand{\cis}{{\tt cis\_interface}{}}
\newcommand{\pkglink}{\todo{cis\_interface}}
%\newcommand{\pkg}{{\tt \todo{cis\_interface}}{}}
\newcommand{\pkgrun}{{\tt yggrun}}
\newcommand{\A}{Appendix{ }}
\newcommand{\hrefgit}[1]{\href{https://github.com/cropsinsilico/cis_interface}{\todo{#1}}}
\newcommand{\hrefdoc}[1]{\href{https://cropsinsilico.github.io/cis_interface/}{\todo{#1}}}
\newcommand{\hrefhack}[1]{\href{https://cropsinsilico.github.io/cis_interface/hackathon2018/index.html}{\todo{#1}}}

%---------------------------------------------------------------------------------
% SOURCE CODE
\newcommand{\rootsrc}{\lstinputlisting[language=C,label={lst:src:root},caption={root.h: Source code for root model in C.}]{../../yggdrasil/examples/root_to_shoot/src/root.h}}
\newcommand{\shootsrc}{\lstinputlisting[language=Python,label={lst:src:shoot},caption={shoot.py: Source code for shoot model in Python.}]{../../yggdrasil/examples/root_to_shoot/src/shoot.py}}

%---------------------------------------------------------------------------------
% WRAPPER CODE
\newcommand{\rootwrap}{\lstinputlisting[language=C,label={lst:wrap:root},caption={root\_wrapper.c: Wrapper source code for root model in C.}]{../../yggdrasil/examples/root_to_shoot/src/root_wrapper.c}}
\newcommand{\shootwrap}{\lstinputlisting[language=Python,label={lst:wrap:shoot},caption={shoot\_wrapper.py: Wrapper source code for shoot model in Python}]{../../yggdrasil/examples/root_to_shoot/src/shoot_wrapper.py}}

%---------------------------------------------------------------------------------
% YAML FILES
\newcommand{\rootyml}{\lstinputlisting[label={lst:yml:root},caption={root.yml: Model YAML specification file for root model.}]{../../yggdrasil/examples/root_to_shoot/root.yml}}
\newcommand{\shootyml}{\lstinputlisting[label={lst:yml:shoot},caption={shoot.yml: Model YAML specification file for shoot model.}]{../../yggdrasil/examples/root_to_shoot/shoot.yml}}
\newcommand{\rootymlfiles}{\lstinputlisting[label={lst:yml:root_files},caption={root\_files.yml: Connection YAML specification file for running the root model in isolation.}]{../../yggdrasil/examples/root_to_shoot/root_files.yml}}
\newcommand{\shootymlfiles}{\lstinputlisting[label={lst:yml:shoot_files},caption={shoot\_files.yml: Model YAML specification file for running the shoot model in isolation.}]{../../yggdrasil/examples/root_to_shoot/shoot_files.yml}}
\newcommand{\intyml}{\lstinputlisting[label={lst:yml:int},caption={root\_to\_shoot.yml: Connection YAML specification file for the root/shoot integration.}]{../../yggdrasil/examples/root_to_shoot/root_to_shoot.yml}}

@@

We present an Open Source Python package, {\pkg}, for creating and running integration networks by connecting existing computational models written in different programming languages. {\pkg} was developed as part of the Crops \emph{in Silico} \citep{Marshall-Colon2017} initiative to build a complete crop \emph{in silico} from the level of the genes to the level of the field. {\pkg} is available on Github\footnote{{\tt https://github.com/cropsinsilico/\pkglink}} with full documentation\footnote{{\tt https://cropsinsilico.github.io/\pkglink/}} and can be installed from PyPI\footnote{{\tt https://pypi.org/project/\pkglink/}} via \todo{\tt pip install {\pkg}} or conda-forge\footnote{{\tt https://github.com/conda-forge/\pkglink-feedstock}} via \todo{\tt conda -c conda-forge install {\pkg}}. Although developed for the purpose of integrating plant biology models, {\pkg} can be applied to any situation requiring coordination between models in the supported languages. \S\ref{S:background} provides background information on existing efforts for cross-language model integration, \S\ref{S:methods} describes the methods used by the {\pkg} package to integrate models, \S\ref{S:example} provides a worked example of integrating the two model presented above, \S\ref{S:results} presents several tests demonstrating the performance of message passing between integrated models, and \S\ref{S:discuss} describes a few use cases for {\pkg}, 
summarizes the features and limitations of the {\pkg} package, and outlines areas of ongoing and future development.
